Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients

### 2020-01-15 RET_Hosts.tex

@@

\section{Host galaxy properties}
\label{sec:analysis} % used for referring to this section from elsewhere
\subsection{Stellar Mass \label{subsec:res_mass}}

>>>>

The host galaxy photometry for the sample of RETs is taken from the catalogue of \citet{Wiseman2020}, which was based upon deep coadds reaching $g$-band limiting magnitudes of 27.

@@

\section{Host galaxy properties}
\label{sec:analysis} % used for referring to this section from elsewhere

To estimate the physical properties of the host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models.

\subsection{Stellar Mass \label{subsec:res_mass}}
